Learning and comparing functional connectomes across subjects

### 2013-01-04 paper.tex
Remove merge mess

% General introduction
Functional connectivity reveals the synchronization of distant neural systems
via correlations in neurophysiological measures of brain activity 
\cite{friston1994, biswal1995}.  Given that
high-level function emerges from the interaction of specialized units,
functional connectivity is an essential part of the description of brain
function, that complements the localizationist picture emerging from the
systematic mapping of regions recruited in tasks\cite{sporns2004}. However,
while there exists a well-defined standard analysis framework for activation
mapping that enables statistically-controlled comparisons across subjects
\cite{friston1995}, group-level analysis of functional connectivity still faces
many open methodological challenges. Deriving a picture of a single subject's
functional connectivity is by itself not straightforward, as the brain comprises
a myriad of interacting subsystems and its connectivity must be decomposed into
simplified and synthetic representations. An important view of brain
connectivity is that of distributed functional networks depicted by their
spatial maps \cite{fox2005}. Another no less important and complementary view is
that of connections linking localized functional modules depicted as a graph
\cite{bullmore2009}. This representation of brain connectivity is often called
the functional connectome \cite{sporns2005} and is the focus of intense
worldwide research efforts as it holds promises of new insights in cognition and
pathologies \cite{greicius2008b,biswal2010,fox2010}.

@@

% Define terms
By ``functional connectome'', here we specifically denote a graph representing
functional interactions in the brain, where the term ``graph'' is taken in its
mathematical sense: a set of \emph{nodes} connected together by \emph{edges}.
Graph nodes (brain region) correspond to a spatially contiguous and functionally
coherent patchs of cortex whose activity is synchronized through
cytoarchitecture and edges describe large range synchronizations between nodes
that are putatively subtended by large fiber pathways \cite{marrelec2006}.  A
graph can be weighted or not, and is completely equivalent to its
\emph{adjacency matrix}, a symmetric matrix tabulating the connection weights
between each pair of nodes.  Functional-connectivity graphs are used to
represent evoked activity, as in task-response studies \cite{mcintosh2000}, as
well as ongoing activity, present in the absence of specific tasks or in the
background during task and often studied in so-called \emph{resting-state}
experiments \cite{raichle2010}. Another important notion that arises from the
study of distributed modes of brain function is that of specialized functional
networks\footnote{In neuroimaging, the term network is sometimes used to denote
	a graph of brain function. To disambiguate the notion of segregated
	spatial mode \cite{fox2005} from that of connectivity graphs, we will
	purposely restrict its usage in this paper.} \cite{fox2005}. With our
definition of the functional connectome, functional networks are not directly
building blocks of the connectome but appear as a consequence of the graphical
structure \cite{varoquaux2010c,varoquaux2012}.

@@

It is important to keep in mind that the proposed correction strategies
are approximate and not definitive techniques. This has become particularly
apparent for head motion with reports that micromovements on the scale
of $\le 0.2$mm can induce artefactual group-level findings even when motion is
accounted for in preprocessing
\cite{vandijk2012,power2011,satterthwaite2012}. Special care must be taken to
adequately control for residual impact of head motion in the group model
\cite{satterthwaite2012, saad2012}.

@@

The choice of regions of interests (ROIs) that define the nodes of the
graphs can be very important both in the estimation of connectomes and
for group comparison \cite{wang2009}. Unsurprisingly, simulations have
shown that extracting signal from ROIs that did not match functional
units would lead to erronous graph estimation \cite{smith2011}.
%
Different strategies to define suitable ROIs coexist. While dense parcellations approaches cover
a large fraction of the brain \cite{achard2006, varoquaux2010c,
wang2009}, this coverage can be traded off to focus on some specific
regions, in favor of increased functional specificity and thus better
% CAMERON I think that this reference to Fair should be Dosenbach 2006 neuron
differentiation across networks \cite{greicius2003, dosenbach2006,
varoquaux2010b}. In addition, while
ROIs are most often defined as a hard selection of voxels, it is also
possible to use a \emph{soft} definition, attributing weights as with
probabilistic atlases, or spatial maps of functional networks extracted
from techniques such as independent component analysis (ICA) \cite{kiviniemi2009,smith2012}.

\paragraph{Regions from atlases}
%
Atlases can be used to define full-brain parcellations. Popular
choices are the the Automatic Anatomic Labeling (AAL) atlas \cite{tzourio-mazoyer2002a}, 
which benefits from an SPM toolbox or the ubiquitous Talaraich-Tournoux
atlas \cite{talaraich}. 
However, these atlases suffer from major
shortcomings; namely \emph{i)} they were defined on a single subject
and thus does does not reflect inter-subject variability, \emph{ii)}
they focus on labeling large anatomical structures and does not match
functional layout --for instance only two regions describe the medial
part of the frontal lobe, and \emph{iii} they are defined based on
cytoarchitectonic or anatomical boundaries and do not incorporate functional
information. Multi-subject probabilistic altases such as the
Harvard-Oxford atlas distributed with FSL \cite{smith2004} or the
sulci-based structural atlas used in \cite{varoquaux2010c} mitigate the
first problem, and the high number of regions defined using sulci also
somewhat circumvent the second problem (see fig.\,\ref{fig:parcellations}).

\paragraph{Defining regions from the literature}
%
Regions can be defined from previous studies, informally or with
systematic meta-analysis. This strategy is used to define the main
resting-state networks, such as the default mode network, but may also be
useful to study connectivity in task-specific networks
% CAMERON include citation to Dosenbach, and some others
\cite{dosenbach2006,grillon2012}. The common practice is to place balls of a given
radius, 5 or 10\,mm, centered at the coordinates of interest. Given that
functional networks are tightly interleaved in some parts of the cortex,
such as the parietal lobe, care must be taken not to define too many
regions that would overlap and lead to mixing of the signal.

\paragraph{FMRI-based function definition}
%
Defining regions directly from the fMRI signal brings many benefits.
First, it can capture subject-specific functional information. Second, it
adapts to the signal at hand and its limitations, such as
image distortions or vascular and movement artifacts that are isolated
in ICA-like approaches. Lastly, incorporating functional information into
regional definition will result in more homogenous regions that better represent
connectivity present at the voxel level then anatomically defined atlases such
as AAL or Harvard-Oxford \cite{craddock2011}. The simplest approach to define task-specific
regions is to use activation maps derived from standard GLM-based
analysis in a task-driven study (see for instance \cite{poldrack2011}).
Regions are extracted by thresholding the maps, or using balls around the
activation peaks. For resting-state studies, unsupervised multivariate
analysis techniques are necessary. Clustering approaches extract
full-brain parcellations \cite{craddock2011, bellec2010, yeo2011,
thirion2006}, and have been shown to segment well-known functional
structures from rest data. Alternatively, decompositions
methods, such as ICA \cite{beckmann2004}, can unmix linear
combinations of multiple effects and separate out overlapping spatial maps
capturing functional networks or confounding effects. At high model
order, ICA maps define a functional parcellation \cite{kiviniemi2009}.
Extracting regions from these maps requires additional effort as they can
display fragmented spatial features and structured background noise, but
incorporating sparsity and spatial constraints in the decomposition
techniques leads to contrasted maps that outline many different
structures \cite{craddock2011, varoquaux2012} (see fig.\,\ref{fig:parcellations}).

%% XX number of regions
% CAMERON added this since it was left to do, I don't know if it really says
% anything 
\paragraph{Optimal number of regions}
%
Defining an optimal number of regions to use for whole brain connectivity analysis bears
careful consideration. On one hand we desire a sufficiently large number of
regions to guarentee that they are functionally homogenous regions and adequately 
represent the connectivity information present in the data. On the other hand
too many regions will result in an explosion in computational complexity 
and interfere with the interpretability of observed connections. For functional
parcellation, cross validation methods can be employed to estimate an optimal 
number of regions based on homogeniety, the ability to reproduce 
connectivity information present at the voxel scale, and the ability to
obtain the same parcellations from independent data 
\cite{craddock2011, germanguy}. In general these metrics do not result in an
obvious peak at a ``best'' number of regions, but instead offer a range over
which the number of regions can be chosen based on the needs of the analysis at
hand.

@@

\caption{
Different full-brain parcellations: the AAL atlas
\cite{tzourio-mazoyer2002a}, the Harvard-Oxford atlas, the sucli atlas used in
\cite{varoquaux2010c}, regions extracted by Ncuts
\cite{craddock2011}, the resting-state networks extracted in
\cite{smith2009} by ICA, and in \cite{varoquaux2011} by sparse dictionary
learning.
\label{fig:parcellations}
}
\end{figure}
%---------------------------------------------------------------------------}}}

@@

\caption{
Correlation matrices of rest time-series extracted from the 39 main
regions of the Varoquaux 2011 \cite{varoquaux2011} parcellation with
different choices of confound regressors -- 
% CAMERON = using CompCor in addition to WM and CSF is redundant as 
% CompCor involves a PCA decomposition of WM and CSF
\textbf{Left}: regressing out CompCor signals, as well as white matter and
CSF average signals and movement parameters. The insert shows the
connections restricted to a few major nodes.
-- \textbf{Upper right}: regressing out only movement parameters. -- 
\textbf{Lower right}:
regressing out movement parameters and global signal mean.
No frequency filtering was applied here.
\label{fig:correlation_matrices}
When no confounding brain signals are regressed, all regions are heavily
correlated. Regressing out common signal, in the form of well-identified
confounds or a global mean, teases out the structure.
}
\end{figure}
%---------------------------------------------------------------------------}}}

% The following paragraph is convoluted: we start to say that rest is
% from time-series, and task from beta, we go on discussing about beta
% maps, and then we move back to rest. It might need restructuring

% Horrible sentence below

\paragraph{Signal extraction}
% CAMERON = I think we should differentiate between signal extraction and signal
% cleaning, actually the cleaning is a seperate issue, that is independent of
% the regions or nodes.
Given a set of graph nodes, the next step is to extract a representative time
series for each node.  To study \emph{intrinsic} activity, \emph{e.g.}\ with
rest data, signal extraction can be acheived by either averaging the fmri time
series across the voxels in a region, or by taking the first eigenvariate from a
principle components analysis of the time series \cite{Friston functional
	localizers}.  The latter approach provides an additional level of
denoising by selecting a time series that explains the greatest variance across
the voxels, and excludes ``deviant'' time series from noise or dissimilar
voxels. Comparisons of these methods has shown that the eigenvariate method is
more sensitive to function inhomogeniety \cite{craddock 2011} and exhibits worse
test-retest reliablity than averaging time series \cite{zuo thingy}. A hybrid
approach would be to average the top few eigenvariates from the PCA
decomposition.  In addition, improved specificity to BOLD signal can be enforced
by using only signal in voxels near gray-matter tissues. For this purpose, we
suggest summarizing the signal in an ROI by a mean of the different voxels
weighted by the subject-specific gray matter probabilistic segmentation, as
output by \emph{e.g.}\ SPM's segmentation tool \cite{ashburner2005}.

@@

% Regressing out task?? Skipping for lack of space
% CAMERON make this better
Estimating intrinsic activity from task based data can be obtained by either
temporally concatenating rest blocks from the task, or by regressing the task
from the fMRI data. The latter approach is justified by the observation that
spontaneous activity is present during and additive to task BOLD responses 
\cite{fox finger tapping}. Evaluations of these methods have shown variable
results, where the resulting connectivity is similar too, but not the same as
results obtained from resting state data \cite{fair, lohman}. The differences 
are likely due to the
large carry over effects seen from task to rest blocks.

@@

For the problem of recovering the functional-connectivity
\emph{structure}, \emph{i.e.}\ finding which region is connected to
which, sparse inverse covariance estimators have been found to be
% CAMERON Isn't there a paper from Stanford about this as well??
efficient \cite{varoquaux2010c, smith2011}. The intuition for relying on
inverse covariance rather than correlation stems from that fact that
standard correlation (marginal correlation) between two variables $a$ and
$b$ also capture the effects of other variables: strong correlation of
$a$ and $b$ with a third variable $c$ will induce a correlation between
$a$ and $b$. On the opposite, the inverse covariance\footnote{Covariance
and correlation matrices differ simply by the fact that a covariance
matrix captures the amplitude of a signal, via its variance, while a
correlation matrix is computed on standardized (zero mean, unit variance) signals.}
matrix captures
partial correlations, removing the effect of other variables
\cite{marrelec2006a}. In the small sample limit, this removal is
challenging from the statistical standpoint, and an assumption of sparsity,
\emph{i.e.}\ that only few variables need to be considered at a time, is
important to estimate a good inverse covariance. Various estimation
strategies exist for sparse inverse covariance, and have an impact on the
resulting networks \cite{varoquaux2012,varoquaux2010c}. The
Graph Lasso ($\ell_1$-penalized maximum-likelihood estimator)
\cite{friedman2008} is in general a good approach for structure recovery. In group studies,
the $\ell_{21}$ estimator \cite{varoquaux2010c,honorio2012} is useful to
impose a common sparsity structure across different subjects and achieve
better recovery of this common structure. Simply put, these approaches
are necessary because estimation noise creates a background structure
(see fig.\,\ref{fig:icov_estimators}); however, unlike in a univariate situation, the
parameters are not independent, and the spurious background connections
degrade the estimation of the actual connections. The sparse estimators
make a compromise between imposing simpler models, \emph{i.e.}\ with less
% CAMERON "fitting well the data" needs to be fixed
connections, and fitting well the data. This compromise is set via a
regularization parameter which controls the sparsity of the estimate. A
good rule of thumb to choose this parameter is via cross-validation
\cite{varoquaux2010c}.

@@

\paragraph{Graph-topology metrics}
%
Functional connectivity graphs have been found to display specific
topological properties\footnote{In the neuroscience world, these
descriptions are grouped under the terms of ``graph theoretical
approaches'', however graph theory is an entire division of mathematics
and computer science that is concerned with much more than topology of
random graphs.} that are characteristic of small-word networks
% CAMERON should cite dani basset
\cite{stam2004,salvador2005,achard2006,bullmore2009}. These networks
display excellent transport properties: although they have a relatively
small number of connections, any two regions of the brain are well
connected. 
% CAMERON cite first small world network science paper
Another interesting consequence of their specific topology is
the resilience it gives the system to attacks such as resulting from
brain lesions \cite{achard2006}. This overall structure of
functional-connectivity graphs can be summarized by a few metrics, such
as the average path length between any two nodes or the local clustering
coefficients \cite{rubinov2010}. Given that pathologies without a
localized focus, such
as schizophrenia, are thought to have a global impact on brain
connectivity \cite{liu2008,bassett2008}, the graph-topology metrics are
promising markers to perform inter-subject comparison. Such an
approach is appealing as it is not subject to multiple comparison issues.
However, it has been criticized as giving a fairly unspecific
characterization of the brain and being fragile to noise
\cite{ioannides2007}. Another caveat is that these properties are not
specific to brain function: correlation matrices display
small-word properties such as local clustering by construction. Indeed, if two
nodes are strongly correlated to a third, they are highly likely to be
correlated to each other \cite{zalesky2012}. This observation highlights
the need for well defined null-hypothesis \cite{zalesky2012,rubinov2011},
but also for controlled recovery of brain functional connectivity going
beyond empirical correlation matrices, as discuss in the previous section.
% CAMERON What about regional summary measures such as centrality??? Xinian's work
% maybe a paragraph that covers ReHo, degree centrality, eigenvector centrality, pagerank etc...

@@

Predictive modeling is concerned with learning (or fitting) a model that is
capable of decoding or \emph{predicting} information from new unseen data
\cite{pereira2009}.  In the context of connectomes, predictive modeling provides
a means for delineating connectivity based biomarkers of disease diagnosis,
prognosis, or other phenotypic outcomes \cite{craddock2009, dosenbach2010}. The
accuracy of a predictive model provides a measure of the amount of information
present in the connectome about the phenotypic measure being evaluated
[kriegeskorte, Kjems].  When combined with reproducibility, prediction accuracy
provides a metric for evaluating experimental tradeoffs for data acquisition,
preprocessing, and analysis [Strother, LaConte].  Multivariate predictive models
are attractive in connectomics because they are sensitive to dependencies
between features and avoid the need to correct for  multiple comparisons since
the significance of an entire pattern is evaluated using a single statistical
test. From the perspective of medical applications, using resting-state
connectivity as a biomarker is particularly appealing as it can be applied to
impaired patients \cite{greicius2008b}. Predictive modeling techniques have been
successfully applied to identify connectome-based biomarkers of Alzheimer's
disease \cite{stonnington2010}, depression \cite{craddock2009}, schizophrenia
\cite{cecchi2009}, autism \cite{anderson2011}, ADHD \cite{zhu2008}, aging
\cite{dosenbach2010}, as well as to classify mental operations
\cite{richiardi2011,shirer2012}.
% CAMERON something about the ADHD200 Global Competition highlights the
% interest/need for predictive modeling in connectomics as well as the number of
% approaches applicable 
Recent work has illustrated the utility of predictive modeling for deriving
connectivity models at the individual level [Chu 2010, Craddock in press or
HBM].

Both the fact that information \emph{can} be
used to make predictions on new data, and \emph{how} it is used or
\emph{where} it lies informs us on brain function.

>>>>

% General introduction
Functional connectivity reveals the synchronization of distant neural systems
via correlations in neurophysiological measures of brain activity 
\cite{friston1993, biswal1995}.  Given that
high-level function emerges from the interaction of specialized units
\cite{tononi1992},
functional connectivity is an essential part of the description of brain
function, that complements the localizationist picture emerging from the
systematic mapping of regions recruited in tasks\cite{sporns2004}. However,
while there exists a well-defined standard analysis framework for activation
mapping that enables statistically-controlled comparisons across subjects
\cite{friston1995}, group-level analysis of functional connectivity still faces
many open methodological challenges. Deriving a picture of a single subject's
functional connectivity is by itself not straightforward, as the brain comprises
a myriad of interacting subsystems and its connectivity must be decomposed into
simplified and synthetic representations. An important view of brain
connectivity is that of distributed functional networks depicted by their
spatial maps \cite{fox2005}. Another no less important and complementary view is
that of connections linking localized functional modules depicted as a graph
\cite{bullmore2009}. This representation of brain connectivity is often called
the functional connectome \cite{sporns2005} and is the focus of intense
worldwide research efforts as it holds promises of new insights in cognition and
pathologies \cite{greicius2008b,biswal2010,fox2010}.

@@

% Define terms
By ``functional connectome'', here we specifically denote a graph representing
functional interactions in the brain, where the term ``graph'' is taken in its
mathematical sense: a set of \emph{nodes} connected together by \emph{edges}.
Graph nodes (brain region) correspond to a spatially contiguous and functionally
coherent patchs of cortex and edges describe large range synchronizations between nodes
that are putatively subtended by large fiber pathways \cite{marrelec2006}.  A
graph can be weighted or not, and is completely equivalent to its
\emph{adjacency matrix}, a symmetric matrix tabulating the connection weights
between each pair of nodes.  Functional-connectivity graphs are used to
represent evoked activity, as in task-response studies \cite{mcintosh2000}, as
well as ongoing activity, present in the absence of specific tasks or in the
background during task and often studied in so-called \emph{resting-state}
experiments \cite{raichle2010}. Another important notion that arises from the
study of distributed modes of brain function is that of specialized functional
networks\footnote{In neuroimaging, the term network is sometimes used to denote
	a graph of brain function. To disambiguate the notion of segregated
	spatial mode \cite{fox2005} from that of connectivity graphs, we will
	purposely restrict its usage in this paper.} \cite{fox2005}. With our
definition of the functional connectome, functional networks are not directly
building blocks of the connectome but appear as a consequence of the graphical
structure \cite{varoquaux2010c,varoquaux2012}.

@@

It is important to keep in mind that the proposed correction strategies
are approximate and not definitive techniques. This has become particularly
apparent for head motion with reports that micromovements on the scale
of $\le 0.2$mm can induce artefactual group-level findings even when motion is
accounted for in preprocessing
\cite{vandijk2012,power2011,satterthwaite2012}. Special care must be taken to
adequately control for residual impact of head motion in the group model
\cite{satterthwaite2012, vandijk2012}.

@@

The choice of regions of interests (ROIs) that define the nodes of the
graphs can be very important both in the estimation of connectomes and
for group comparison \cite{wang2009}. Unsurprisingly, simulations have
shown that extracting signal from ROIs that did not match functional
units would lead to erronous graph estimation \cite{smith2011}.
%
Different strategies to define suitable ROIs coexist. While dense parcellations approaches cover
a large fraction of the brain \cite{achard2006, varoquaux2010c,
wang2009,bellec2006}, this coverage can be traded off to focus on some specific
regions, in favor of increased functional specificity and thus better
differentiation across networks \cite{greicius2003, dosenbach2006,
varoquaux2010b}. In addition, while
ROIs are most often defined as a hard selection of voxels, it is also
possible to use a \emph{soft} definition, attributing weights as with
probabilistic atlases, or spatial maps of functional networks extracted
from techniques such as independent component analysis (ICA) \cite{kiviniemi2009,smith2012}.

\paragraph{Regions from atlases}
%
Atlases can be used to define full-brain parcellations. Popular
choices are the Automatic Anatomic Labeling (AAL) atlas \cite{tzourio-mazoyer2002a}, 
which benefits from an SPM toolbox or the ubiquitous Talaraich-Tournoux
atlas \cite{talaraich1988}. 
However, these atlases suffer from major
shortcomings; namely \emph{i)} they were defined on a single subject
and thus does does not reflect inter-subject variability, \emph{ii)}
they focus on labeling large anatomical structures and do not match
functional layout --for instance only two regions describe the medial
part of the frontal lobe, and \emph{iii} they are defined based on
cytoarchitectonic or anatomical boundaries and do not incorporate functional
information. Multi-subject probabilistic altases such as the
Harvard-Oxford atlas distributed with FSL \cite{smith2004} or the
sulci-based structural atlas used in \cite{varoquaux2010c} mitigate the
first problem, and the high number of regions defined using sulci also
somewhat circumvent the second problem (see fig.\,\ref{fig:parcellations}).

\paragraph{Defining regions from the literature}
%
Regions can be defined from previous studies, informally or with
systematic meta-analysis. This strategy is used to define the main
resting-state networks, such as the default mode network, but may also be
useful to study connectivity in task-specific networks
\cite{biswal1995,rissman2004,dosenbach2006,grillon2012}. The common practice is to place balls of a given
radius, 5 or 10\,mm, centered at the coordinates of interest. Given that
functional networks are tightly interleaved in some parts of the cortex,
such as the parietal lobe, care must be taken not to define too many
regions that would overlap and lead to mixing of the signal.

\paragraph{FMRI-based function definition}
%
Defining regions directly from the fMRI signal brings many benefits.
First, it can capture subject-specific functional information. Second, it
adapts to the signal at hand and its limitations, such as
image distortions or vascular and movement artifacts that are isolated
in ICA-like approaches. Lastly, incorporating functional information into
regional definition will result in more homogenous regions that better represent
connectivity present at the voxel level then anatomically defined atlases such
as AAL or Harvard-Oxford \cite{craddock2012}. The simplest approach to define task-specific
regions is to use activation maps derived from standard GLM-based
analysis in a task-driven study (see for instance \cite{poldrack2011}).
Regions are extracted by thresholding the maps, or using balls around the
activation peaks. For resting-state studies, unsupervised multivariate
analysis techniques are necessary. Clustering approaches extract
full-brain parcellations \cite{craddock2012,bellec2010,yeo2011,thirion2006}, and have been shown to segment well-known functional
structures from rest data. Alternatively, decompositions
methods, such as ICA \cite{beckmann2004}, can unmix linear
combinations of multiple effects and separate out overlapping spatial maps
capturing functional networks or confounding effects. At high model
order, ICA maps define a functional parcellation \cite{kiviniemi2009}.
Extracting regions from these maps requires additional effort as they can
display fragmented spatial features and structured background noise, but
incorporating sparsity and spatial constraints in the decomposition
techniques leads to contrasted maps that outline many different
structures \cite{varoquaux2012} (see fig.\,\ref{fig:parcellations}).

%% XXX number of regions
% CAMERON added this since it was left to do, I don't know if it really says
% anything 
\paragraph{Optimal number of regions}
%
Defining an optimal number of regions to use for whole brain connectivity analysis bears
careful consideration. On one hand we desire a sufficiently large number of
regions to guarentee that they are functionally homogenous regions and adequately 
represent the connectivity information present in the data. On the other hand
too many regions will result in an explosion in computational complexity 
and interfere with the interpretability of observed connections. For functional
parcellation, cross validation methods can be employed to estimate an optimal 
number of regions based on homogeniety, the ability to reproduce 
connectivity information present at the voxel scale, and the ability to
obtain the same parcellations from independent data 
\cite{craddock2012, blumensath2012}. In general these metrics do not result in an
obvious peak at a ``best'' number of regions, but instead offer a range over
which the number of regions can be chosen based on the needs of the analysis at
hand.

@@

\caption{
Different full-brain parcellations: the AAL atlas
\cite{tzourio-mazoyer2002a}, the Harvard-Oxford atlas, the sucli atlas used in
\cite{varoquaux2010c}, regions extracted by Ncuts
\cite{craddock2012}, the resting-state networks extracted in
\cite{smith2009} by ICA, and in \cite{varoquaux2011} by sparse dictionary
learning.
\label{fig:parcellations}
}
\end{figure}
%---------------------------------------------------------------------------}}}

@@

\caption{
Correlation matrices of rest time-series extracted from the 39 main
regions of the Varoquaux 2011 \cite{varoquaux2011} parcellation with
different choices of confound regressors -- 
\textbf{Left}: regressing out CompCor signals, as well as white matter and
CSF average signals and movement parameters. The insert shows the
connections restricted to a few major nodes.
-- \textbf{Upper right}: regressing out only movement parameters. -- 
\textbf{Lower right}:
regressing out movement parameters and global signal mean.
No frequency filtering was applied here.
\label{fig:correlation_matrices}
When no confounding brain signals are regressed, all regions are heavily
correlated. Regressing out common signal, in the form of well-identified
confounds or a global mean, teases out the structure.
}
\end{figure}
%---------------------------------------------------------------------------}}}

\paragraph{Signal extraction and cleaning}
Given a set of graph nodes, the next step is to extract a representative time
series for each node.  To study \emph{intrinsic} activity, \emph{e.g.}\ with
rest data, signal extraction can be achieved by either averaging the fMRI time
series across the voxels in a region, or by taking the first eigenvariate from a
principle components analysis of the time series \cite{Friston functional
	localizers}.
Comparisons of these methods has shown that the eigenvariate method is
more sensitive to function inhomogeneity \cite{craddock2012} and exhibits worse
test-retest reliablity than averaging time series \cite{zuo2010}. 
In addition, improved specificity to BOLD signal can be enforced
by using only signal in voxels near gray-matter tissues. For this purpose, we
suggest summarizing the signal in an ROI by a mean of the different voxels
weighted by the subject-specific gray matter probabilistic segmentation, 
as output by \emph{e.g.}\ SPM's segmentation tool \cite{ashburner2005} or
FSL's FAST program \cite{zhang2001}.

With rest dataset, it is important to regress out time series capturing
movement and other sources of structured noise, to separate on-going
activity from confounding signals. In addition to removing movement
parameters estimated during preprocessing, removing linear trends, signal
extracted from the white matter and the CSF \cite{chang2009}, as well as
using the CompCor \cite{behzadi2007} procedure gives more contrasted
correlation matrices that outline functional structures better
(fig.\,\ref{fig:correlation_matrices}). 
Indeed, white matter and CSF signals capture thermal noise, 
systematic variation due to multichannel head coils, cardiac and resp.
smaller motions, physiological noise correction.
Filtering high frequencies is
often recommended, based on the initial observation that neural-related
signals are observed below 0.1\,Hz \cite{cordes2001,biswal1995}. While
high-pass and low-pass filtering decrease the impact of some confounds,
recent studies have shown that information on neural processes is present
in the full spectrum of frequencies observed
\cite{smith2012,vanoort2012}. Regressing out a good choice of confound
signals is more specific than frequency filter, and in our experience
gives more contrasted correlation matrices\footnote{Note that naive use
of filtering can induce spurious correlations \cite{davey2012}.}.
Finally, it is important to keep in mind that using resting-state to
study on-going activity is fragile to confounds such as movement
\cite{vandijk2012,power2011} or scanner noise, and probably more so than
activation studies as it is harder to control the specificity of the
signal extracted. Special care must be taken in preprocessing strategies
\cite{vandijk2010,satterthwaite2012}.

@@

% Regressing out task?? Skipping for lack of space
% I'd rather skip it, as I really do not believe it actually works, and
% would like to stay out of a controversy

@@

For the problem of recovering the functional-connectivity
\emph{structure}, \emph{i.e.}\ finding which region is connected to
which, sparse inverse covariance estimators have been found to be
% CAMERON Isn't there a paper from Stanford about this as well??
% GAEL: I cannot find it with a quick Google. Do you have a name?
% CAMERON: I think that it is ryali 2011, added
efficient \cite{varoquaux2010c, ryali2011, smith2011}. The intuition for relying on
inverse covariance rather than correlation stems from that fact that
standard correlation (marginal correlation) between two variables $a$ and
$b$ also capture the effects of other variables: strong correlation of
$a$ and $b$ with a third variable $c$ will induce a correlation between
$a$ and $b$. On the opposite, the inverse covariance\footnote{Covariance
and correlation matrices differ simply by the fact that a covariance
matrix captures the amplitude of a signal, via its variance, while a
correlation matrix is computed on standardized (zero mean, unit variance) signals.}
matrix captures
partial correlations, removing the effect of other variables
\cite{marrelec2006a}. In the small sample limit, this removal is
challenging from the statistical standpoint, and an assumption of sparsity,
\emph{i.e.}\ that only few variables need to be considered at a time, is
important to estimate a good inverse covariance. Various estimation
strategies exist for sparse inverse covariance, and have an impact on the
resulting networks \cite{varoquaux2012,varoquaux2010c}. The
Graph Lasso ($\ell_1$-penalized maximum-likelihood estimator)
\cite{friedman2008} is in general a good approach for structure recovery. In group studies,
the $\ell_{21}$ estimator \cite{varoquaux2010c,honorio2012} is useful to
impose a common sparsity structure across different subjects and achieve
better recovery of this common structure. Simply put, these approaches
are necessary because estimation noise creates a background structure
(see fig.\,\ref{fig:icov_estimators}); however, unlike in a univariate situation, the
parameters are not independent, and the spurious background connections
degrade the estimation of the actual connections. The sparse estimators
make a compromise between imposing simpler models, \emph{i.e.}\ with less
% CAMERON "fitting well the data" needs to be fixed
connections, and fitting well the data. This compromise is set via a
regularization parameter which controls the sparsity of the estimate. A
good rule of thumb to choose this parameter is via cross-validation
\cite{varoquaux2010c}.

@@

\paragraph{Graph-topology metrics}
%
Functional connectivity graphs have been found to display specific
topological properties\footnote{In the neuroscience world, these
descriptions are grouped under the terms of ``graph theoretical
approaches'', however graph theory is an entire division of mathematics
and computer science that is concerned with much more than topology of
random graphs.} that are characteristic of small-word networks
% CAMERON should cite dani basset
\cite{stam2004,salvador2005,achard2006,bullmore2009}. These networks
display excellent transport properties: although they have a relatively
small number of connections, any two regions of the brain are well
connected. 
% CAMERON cite first small world network science paper
Another interesting consequence of their specific topology is
the resilience it gives the system to attacks such as resulting from
brain lesions \cite{achard2006}. This overall structure of
functional-connectivity graphs can be summarized by a few metrics, such
as the average path length between any two nodes, the local clustering
coefficients, or the node degree centrality \cite{rubinov2010}. Given that pathologies without a
localized focus, such
as schizophrenia, are thought to have a global impact on brain
connectivity \cite{liu2008,bassett2008}, the graph-topology metrics are
promising markers to perform inter-subject comparison. Such an
approach is appealing as it is not subject to multiple comparison issues.
However, it has been criticized as giving a fairly unspecific
characterization of the brain and being fragile to noise
\cite{ioannides2007}. Another caveat is that these properties are not
specific to brain function: correlation matrices display
small-word properties such as local clustering by construction. Indeed, if two
nodes are strongly correlated to a third, they are highly likely to be
correlated to each other \cite{zalesky2012}. This observation highlights
the need for well defined null-hypothesis \cite{zalesky2012,rubinov2011},
but also for controlled recovery of brain functional connectivity going
beyond empirical correlation matrices, as discuss in the previous section.
% CAMERON What about regional summary measures such as centrality??? Xinian's work
% maybe a paragraph that covers ReHo, degree centrality, eigenvector centrality, pagerank etc...

@@

Predictive modeling is concerned with learning (or fitting) a model that is
capable of decoding or \emph{predicting} information from new unseen data
\cite{pereira2009}.  In the context of connectomes, predictive modeling provides
a means for delineating connectivity based biomarkers of disease diagnosis,
prognosis, or other phenotypic outcomes \cite{craddock2009, dosenbach2010}. The
accuracy of a predictive model provides a measure of the amount of information
present in the connectome about the phenotypic measure being evaluated
\cite{kjems2002, kriegeskorte2006}.  When combined with reproducibility, prediction accuracy
provides a metric for evaluating experimental tradeoffs for data acquisition,
preprocessing, and analysis \cite{strother2002, laconte2003}.  Multivariate
predictive modeling (MPM)
are attractive in connectomics because they are sensitive to dependencies
between features and avoid the need to correct for multiple comparisons since
the significance of an entire pattern is evaluated using a single statistical
test. 
Additionally many modern MPM techniques exist which are specifically
formulated to deal with high dimensional datasets with few observations.
Predictive modeling techniques have been
successfully applied to identify connectome-based biomarkers of Alzheimer's
disease \cite{stonnington2010}, depression \cite{craddock2009, zeng2012}, schizophrenia
\cite{cecchi2009}, autism \cite{anderson2011}, ADHD \cite{zhu2008,}, aging
\cite{dosenbach2010}, as well as to classify mental operations
\cite{richiardi2011,shirer2012}. The growing interest for applying MPM 
to connectivity analysis was highlighted by the ADHD200
Global Competition, in which the object was to identify a connectivity based
biomarker of ADHD \cite{adhd2002012}. Recent work has illustrated the utility
of predictive modeling for deriving connectivity models at the individual level
\cite{chu2011}.
